Check Coverage

### 2019-11-21 analysis/merge_data.Rmd
First attempt at correction via a simple glm.

Are there any studies for which we have trait data for all species?
```{r}
merge_data <- function(trait_data){
  biotime_data %>%
    select(-sourceName, -scientificName) %>%
  left_join(trait_data, by = "id",
            na_matches = "never") %>%
    drop_na(scientificName)
}
```

Get data w/traits for all studies that have >85% trait coverage
```{r}
#set coverage threshold for analysis dataset
percent <- 0.85

@@

#this gives a coverage for each trait dataset, so potentially a lot of coverage with one dataset and no coverage on all the rest
#need to get rid of zeros when there is coverage from another dataset so we only have one entry per study
coverage <- comp_biotime_traits %>%
  group_by(study_id) %>%
  summarise(perc = sum(!is.na(sourceName))/n()) %>%
  arrange(desc(perc))

@@

biotime_traits <- comp_biotime_traits %>%
  filter(study_id %in% inc_coverage$study_id, !is.na(sourceName))
```

>>>>

Are there any studies for which we have trait data for all species?
```{r}
merge_data <- function(trait_data){
  biotime_data %>%
    select(-scientificName) %>%
    rename(biotimeName = sourceName) %>%
  left_join(trait_data %>% rename(traitName = sourceName), by = "id",
            na_matches = "never") #%>%
   # drop_na(scientificName)
}
```

Get data w/traits for all studies that have >85% trait coverage

`id` is `NA` if there was no `id` match
`biotimeName` or `traitName` is `NA` if that ID is the result of an average of multliple species matches
`scientificName` is `NA` when there was no trait data for a given ID
```{r}
#set coverage threshold for analysis dataset
percent <- 0.85

@@

#this gives a coverage for each trait dataset, so potentially a lot of coverage with one dataset and no coverage on all the rest
#need to get rid of zeros when there is coverage from another dataset so we only have one entry per study
coverage <- comp_biotime_traits %>%
  select(study_id, scientificName) %>%
  distinct() %>%
  group_by(study_id) %>%
  summarise(perc = sum(!is.na(scientificName))/n()) %>%
  arrange(desc(perc))

@@

biotime_traits <- comp_biotime_traits %>%
  filter(study_id %in% inc_coverage$study_id, !is.na(scientificName)) #get studies with appropriate coverage and drop observations that we don't have trait data for
```
